Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses

### 2013-11-08 masters/body/masters.tex
dunno

\section{Results}
\label{sec:results}
This section contains results of the proposed texture mapping process
on a number of different environments, with geometry generated from
three different models. Further images of individual textured
surfaces and entire textured models, as well as videos and interactive
walkthroughs can also be found at
\footnote{\url{http://www-video.eecs.berkeley.edu/research/indoor/}}.

\subsection{Examples}
\label{sec:examples}
As mentioned in Section \ref{sec:dataAcquisition}, the texture mapping
procedure in this thesis can be applied both to low-resolution and
high-resolution models. Low resolution models have an advantage in
their simplicity, and in that only important environmental features
are represented. As a result, images are generated for large sections
of buildings, and boundaries between each texture are minimally
visible. High resolution models have an obvious advantage in terms of
the amount of detail that can be reconstructed, but with poor region
partitioning, as described in Section \ref{sec:geometryPartitioning},
or with high camera pose or geometry reconstruction error, 3D elements
in the environment geometry may not match up well with their imaged
counterparts.

\begin{figure}
  \centering
  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_v.png}
  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_2d.png}
  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_3d.png}\\
  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_v.png}
  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_2d.png}
  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_3d.png}\\
  \subfloat[][]{
    \includegraphics[width=2.1in,height=2in]{results_swarm_5_v.png}
  } \subfloat[][]{
    \includegraphics[width=2.1in,height=2in]{results_swarm_5_2d.png}
  } \subfloat[][]{
    \includegraphics[width=2.1in,height=2in]{results_swarm_5_3d.png}
  }
  \caption{The same indoor environments, as generated using (a) PCA
    plane-fitting, (b) Floor plan extrusion, (c) Watertight mesh
    generation. The first two are low-resolution models, while the
    third is high-resolution}
  \label{fig:modelcomparisons}
\end{figure}

Our approach was tested with three different geometry-reconstruction
methods, a PCA-based plane-fitting method \cite{sanchez2012point}, a
floor plan extrusion method \cite{turnerfloorplan}, and a
voxel-carving mesh generation method \cite{turnerwatertight}. The
first two methods generate lower-resolution models, containing only
major walls, ceilings and floors. The third method generates
high-resolution models, and attempts to reconstruct all scanned
objects in the environment. A comparison of all three methods as
applied to the same dataset is shown in Figure
\ref{fig:modelcomparisons}

@@

\begin{figure}
  \centering
  \includegraphics[width=3.1in]{results_houston_1_2d.png}
  \includegraphics[width=3.1in]{results_houston_1_3d.png}\\
  \includegraphics[width=3.1in]{results_houston_2_2d.png}
  \includegraphics[width=3.1in]{results_houston_2_3d.png}\\
  \subfloat[][]{
    \includegraphics[width=3.1in]{results_houston_3_2d.png}
  } \subfloat[][]{
    \includegraphics[width=3.1in]{results_houston_3_3d.png}
  }
  \caption{(a) A model generated by the low-resolution floor plan
    method. (b) A model generated by the high-resolution voxel-carving
    method.}
  \label{fig:2dvs3d}
\end{figure}

@@

As visible in Figure \ref{fig:2dvs3d} and other images in this
section, 2D models using the floor plan approach are generally
preferred, as they provide enough detail in geometry to reconstruct
the basic layout of an environment, while textures can be used to
visualize smaller details. On the other hand, for applications where
furniture and smaller interior details are important, applying
textures to the 3D voxel-carved models provides useful image-based
context for visualizing indoor areas. Further examples of
texture-mapped models are contained at the end of this
document. Figure \ref{fig:indivPlanes} contains textured surfaces
alone. Figures \ref{fig:victor1}-\ref{fig:e2d4} contain interior and
exterior views of low-resolution models. Figures
\ref{fig:e3d1}-\ref{fig:e3d4} contain interior and exterior views of
high-resolution models.

@@

\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston3.png}
  }
  \caption{A textured low-resolution model from the floor plan extrusion approach.}
  \label{fig:e2d1}
\end{figure}

@@

\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{office.png} \\
    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston3.png}
  }
  \caption{A textured low-resolution model from the floor plan extrusion approach.}
  \label{fig:e2d3}
\end{figure}

\begin{figure}
  \centering{
    \includegraphics[width=6in,height=1.7in]{coryf2.jpg}\\
    \includegraphics[width=6in,height=1.7in]{houston1.jpg}
  }
  \caption{Further exterior views of textured models.}
  \label{fig:e2d4}
\end{figure}

\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston3.png}
  }
  \caption{A textured high-resolution model from the voxel-carving approach.}
  \label{fig:e3d1}
\end{figure}
\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{coryf2_3d_1.png} \\
    \includegraphics[width=6.2in,height=3in]{coryf2_3d_2.png} \\
    \includegraphics[width=6.2in,height=3in]{coryf2_3d_3.png}
  }
  \caption{A textured high-resolution model from the voxel-carving approach.}
  \label{fig:e3d2}
\end{figure}
\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston3.png}
  }
  \caption{A textured high-resolution model from the voxel-carving approach.}
  \label{fig:e3d3}
\end{figure}
\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston3.png}
  }
  \caption{A textured high-resolution model from the voxel-carving approach.}
  \label{fig:e3d4}
\end{figure}

>>>>

\section{Results}
\label{sec:results}
This section contains results of the proposed texture mapping process
on a number of different environments, with geometry generated using
three different methods. Further images of individual textured
surfaces and entire textured models, as well as videos and interactive
walkthroughs can also be found at
\footnote{\url{http://www-video.eecs.berkeley.edu/research/indoor/}}.

\subsection{Examples}
\label{sec:examples}
As mentioned in Section \ref{sec:dataAcquisition}, the texture mapping
procedure in this thesis can be applied both to low-resolution and
high-resolution models. Low resolution models have an advantage in
their simplicity, and in that only important environmental features
are represented. As a result, images are generated for large sections
of buildings, and texture continuity is maintained over large
areas. High resolution models have an obvious advantage in terms of
the amount of detail that can be reconstructed, but with poor region
partitioning, as described in Section \ref{sec:geometryPartitioning},
or with high camera pose or geometry reconstruction error, 3D elements
in the environment geometry may not match up well with their imaged
counterparts.

\begin{figure}
  \centering
  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_v.png}
  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_2d.png}
  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_3d.png}\\
  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_v.png}
  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_2d.png}
  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_3d.png}\\
  \subfloat[][]{
    \includegraphics[width=2.1in,height=2in]{results_swarm_5_v.png}
  } \subfloat[][]{
    \includegraphics[width=2.1in,height=2in]{results_swarm_5_2d.png}
  } \subfloat[][]{
    \includegraphics[width=2.1in,height=2in]{results_swarm_5_3d.png}
  }
  \caption{The same indoor environments, as generated using (a) PCA
    plane-fitting, (b) Floor plan extrusion, (c) Voxel carving. The
    first two are low-resolution models, while the third is
    high-resolution. The PCA method is not watertight, and contains
    some holes (white). It also has the lowest level of detail in its
    geometry. The floor plan method is slightly more detailed, and is
    watertight as well. The voxel carving method also produces
    watertight meshes, and reconstructs smaller features, such as the
    bench and the ladder in the lower two images.}
  \label{fig:modelcomparisons}
\end{figure}

Our approach was tested with three different geometry-reconstruction
methods, a PCA-based plane-fitting method \cite{sanchez2012point}, a
floor plan extrusion method \cite{turnerfloorplan}, and a
voxel-carving mesh generation method \cite{turnerwatertight}. The
first two methods generate lower-resolution models, containing only
major walls, ceilings and floors. The third method generates
high-resolution models, and attempts to reconstruct all scanned
objects in the environment. Images illustrating the differences
between the three methods are in Figure \ref{fig:modelcomparisons}

@@

\begin{figure}
  \centering
  \includegraphics[width=3.1in]{results_houston_1_2d.png}
  \includegraphics[width=3.1in]{results_houston_1_3d.png}\\
  \includegraphics[width=3.1in]{results_houston_2_2d.png}
  \includegraphics[width=3.1in]{results_houston_2_3d.png}\\
  \subfloat[][]{
    \includegraphics[width=3.1in]{results_houston_3_2d.png}
  } \subfloat[][]{
    \includegraphics[width=3.1in]{results_houston_3_3d.png}
  }
  \caption{(a) A model generated by the low-resolution floor plan
    method. (b) A model generated by the high-resolution voxel-carving
    method. The high-resolution model contains far more surface
    detail, such as in the ceiling indentations or the benches on the
    ground. In terms of producing a realistic visualization however,
    the low-resolution model performs very similarly to the
    high-resolution model.}
  \label{fig:2dvs3d}
\end{figure}

@@

As visible in Figure \ref{fig:2dvs3d} and other images in this
section, 2D models using the floor plan approach are generally
preferred, as they provide enough detail in geometry to reconstruct
the basic layout of an environment, while textures can be used to
visualize smaller details. On the other hand, for applications where
furniture and smaller interior details are important, applying
textures to the 3D voxel-carved models provides useful image-based
context for visualizing indoor areas. Further examples of
texture-mapped models are contained at the end of this
document. Figure \ref{fig:indivPlanes} contains textured surfaces
alone. Figures \ref{fig:victor1}-\ref{fig:e2d4} contain interior and
exterior views of low-resolution models. Figures
\ref{fig:e3d1}-\ref{fig:e3d3} contain interior and exterior views of
high-resolution models.

@@

\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{houston2d1.png} \\
    \includegraphics[width=6.2in,height=3in]{houston2d2.png} \\
    \includegraphics[width=6.2in,height=3in]{houston3.png}
  }
  \caption{A textured low-resolution model from the floor plan extrusion approach.}
  \label{fig:e2d1}
\end{figure}

@@

\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{office.png} \\
    \includegraphics[width=6.2in,height=3in]{office1.png} \\
    \includegraphics[width=6.2in,height=3in]{office2.png}
  }
  \caption{A textured low-resolution model from the floor plan extrusion approach.}
  \label{fig:e2d3}
\end{figure}

\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{bhh1.png} \\
    \includegraphics[width=6.2in,height=3in]{bhh2.png} \\
    \includegraphics[width=6.2in,height=3in]{bhh3.png}
  }
  \caption{A textured low-resolution model from the floor plan extrusion approach.}
  \label{fig:e2d4}
\end{figure}

\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
    \includegraphics[width=6.2in,height=3in]{houston3d2.png}
  }
  \caption{A textured high-resolution model from the voxel-carving approach.}
  \label{fig:e3d1}
\end{figure}
\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{coryf2_3d_4.png} \\
    \includegraphics[width=6.2in,height=3in]{coryf2_3d_2.png} \\
    \includegraphics[width=6.2in,height=3in]{coryf2_3d_3.png}
  }
  \caption{A textured high-resolution model from the voxel-carving approach.}
  \label{fig:e3d2}
\end{figure}
\begin{figure}
  \centering{
    \includegraphics[width=6.2in,height=3in]{bhh3d1.png} \\
    \includegraphics[width=6.2in,height=3in]{bhh3d2.png} \\
    \includegraphics[width=6.2in,height=3in]{bhh3d3.png}
  }
  \caption{A textured high-resolution model from the voxel-carving approach.}
  \label{fig:e3d3}
\end{figure}
